---
title: "Which Wine?"
output:
html_document:
theme: cerulean
---

<style type="text/css">

body{ /* Normal  */
      font-size: 16px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 16px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>
---


I am consistently being asked by my friends if there is any wine that I recommend them to buy. However, there are so many features to consider when answering such questions, for example, dry v.s. sweet, price, white or red, etc. Inspired by those questions, I made this series of visualization, aiming to help my friends and audiences like you to choose the next bottle to buy. Hopefully the visualizations can help you decide which wines to be on the shopping list. Enjoy!


(Clicking the tabs on top allows to see a larger view of the viz)



# Plot 1 The Global Wine Industry
```{r,echo=FALSE,warning = FALSE,out.height = 500,out.width=800}
library(knitr)
knitr::include_url("plot1.html")
```


This viz would show the distribution of wineries in the world. There are around 4,000 producers in my dataset, and mainly located in Eastern Europe, the U.S., Southern parts of South America and Africa, and Australia.


By moving the mouse, you can see the hover information of producers and products in each country.



# Plot 2 Wine Types and Varieties
```{r,echo=FALSE,warning = FALSE,out.height = 800,out.width=650}
library(knitr)
knitr::include_url("plot2.html")
```


Wines are categorized into red, white, rose, and sparkling. There are hard and fortified wines as well, featuring with very high abv (~40), which do not enjoy a large group of consumers compared to the 4 types of wines mentioned above.


By using the dropdown button, you may select a type of wine and start to explore the abv and degree of the wines and what main grape variety they are made by. 

“Variety” is the category you want to use when looking for products. For example, if you are entering Trader Joe’s, you may see signs of “Cabernet Sauvignon”, “Chardonnay”, and “Merlot” on the shelf of wines. Those are the (main) grape variety of the wine.


Abv, or alcohol by volume, is the measurement of how much alcohol it contains in each unit. In practice, some wines have an abv range instead of the exact value, such as “11% - 13%”. Degree, or the serving temperature, can be vary among types and grape varieties as well. For example, sparkling is better to be served iced cold.


We can start by looking at the red wine type, which I believe has the most products. In this type, wines made by different grape varieties have a similar degree and abv. Cabernet Sauvignon has a small variation in abv, while Grenache has a larger variation, from 9 to 17. If we start to explore other types of wines, Moscato can be used for both white and sparkling, and the abv of this variety is low, from 2 to 7, which would be favored by people who cannot handle a lot of alcohol (like my roommate).



# Plot 3 Detailed Features
### After gaining a basic understanding of different varieties, you may expect some more detailed information. 
```{r,echo=FALSE,warning = FALSE,out.height = 900,out.width=800}
library(knitr)
knitr::include_url("plot3.html")
```



This view links the three views together. When looking at the top-left one (abv & degree), you can brush an area of product, and the following views would highlight other information including sweet, acidity, body, and tannin.


For example, if you like sweet and do not like sour, you can start with the top right plot (sweet & sour), and select the bottom-right part (sweetness is high while acidity is low). After that, Moscato and Chardonnay would be highlighted and there is a slight difference in body for those two grape varieties, which you can chooce accordingly.


# Plot 4 Price over Time
### At this stage, have you decided which variety is your favorite? Now, let’s dive into the products and choose something to buy!
```{r,echo=FALSE,warning = FALSE,out.height = 900,out.width=900}
library(knitr)
knitr::include_url("plot4.html")
```





Price would vary in different years. By choosing a variety, you can look at the average price of the variety for producers in different countries from 2001 to 2019. For example, France has really pricy Pinot Noir and Chardonnay, while the U.S. has expensive Cabernet Sauvignon, which has an increase in price after 2014. By moving your mouse to a line, the line which represents a country would be highlighted to help you see the trend clearly. 


Aside from the average price, you may also look at the price distribution. Taking Sauvignon Blanc as an example, Chile has the most products and the prices are relatively low, while the products from France and the U.S. have a wide price range. 


# Plot 5 Reviews
### However, does expensive mean good? 
```{r,echo=FALSE,warning = FALSE,out.height = 600,out.width=1100}
library(knitr)
knitr::include_url("plot5.html")
```



I believe most of us would like to buy products that are in high quality and fairly priced.


In the final visualization, you can explore the price and review of different products. The review is from WineEnthusiast. Again, the dropdown allows you to choose a specific country and variety to look at. The price slider at the very bottom allows to choose a price range, and the view at top would only show product in that price range. By hovering you can also look at the product name and what people comment about the product. 


For me, I would like to try a South Africa Chardonnay. I may consider Neil Ellis 2011 which is $28 and scored 91/100, and the rich fruit flavors mentioned in the review appeals me.



### We are approaching the end of the wine exploration journey, did you add any bottle on your shopping list? :)